Relational Parametricity for Algebraically Indexed Types

### 2012-06-12 paper/section-instantiations.tex
Add AUCTeX commands to deal with multifile document
Substantial changes to the motivating examples section
Major changes
- Refined set of contributions
- "Complete" the motivating examples section
- Fill in some references for the background section
- "Complete" the general framework section
- Sketch the "consequences" section
- Sketch the "discussion" section

\section{Instantiations of the General Framework}
\label{sec:instantiations}

\subsection{Multiplicative Group Examples}
\label{sec:multiplicative-examples}

\subsection{Additive Group Examples}
\label{sec:additive-examples}

\subsection{Logic Examples}
\label{sec:logic-examples}

>>>>

\section{Consequences of the Abstraction Theorem}
\label{sec:instantiations}

\fixme{explain the general setup, with a set of operations for each
  instantiation.}

\subsection{Theorems for Free}
\label{sec:theorems-for-free}

Wadler's influential ``Theorems for Free!''  \cite{wadler89theorems}
emphasised a particular aspect of Reynolds' theory of relational
parametricity: the fact that we can read off theorems about a program
simply by looking at the relational interpretation of its type. We now
state some free theorems that are derivable in each of the three main
examples we introduced in \autoref{sec:motivating-examples}.

\subsubsection{Two-Dimensional Geometry}
\label{sec:geometry-consequences}

(In)variance properties

\subsubsection{Logical Information Flow}
\label{sec:information-flow-consequences}

Non-interference properties

\subsubsection{Metric Spaces}
\label{sec:metric-space-consequences}

Continuity via $\epsilon$-$\delta$ proofs.

\subsection{Types Indexed by Abelian Groups}
\label{sec:types-indexed-abelian-groups}

\begin{enumerate}
\item Two cases: when we have a total ``division'' operation, and when
  we don't.
\item Type isomorphisms, based on Smith Normal Form
\item Non-definability results, based on the non-compositional
  relational environments
\item Alteration of the non-definability results in the light of
  addition of a square root operation
\item Mention the variation we can obtain by changing some types,
  e.g. the type of $\mathrm{abs}$. Also, the complex numbers example.
\end{enumerate}

%%% Local Variables:
%%% TeX-master: "paper"
%%% End:

### 2012-06-12 paper/section-introduction.tex
Major changes
- Refined set of contributions
- "Complete" the motivating examples section
- Fill in some references for the background section
- "Complete" the general framework section
- Sketch the "consequences" section
- Sketch the "discussion" section

There are three main points to get across:
\begin{enumerate}
\item Why algebraically indexed types?
\item Why relational parametricity?
\item Why study them together?
\end{enumerate}

@@

>>>>

% Possible angles of attack:
% \begin{itemize}
% \item Parametric polymorphic types allow us to prevent
%   over-specification of the behaviour of programs. For instance, the
%   type $\forall \alpha. [\alpha] \to [\alpha]$ is a generalisation of
%   the types $[\mathsf{int}] \to [\mathsf{int}]$ and $[\mathsf{char}]
%   \to [\mathsf{char}]$. Either of the latter two types over-specify
%   the behaviour of the function.
% \item There are other cases of programs that are over-specified. The
%   leading example we just below is of geometric programs that
%   manipulate coordinate data. Often, programs that manipulate
%   coordinate data are insensitive to geometric transformations. For
%   example, a program that computes the area of a triangle described by
%   three points is insensitive to translations or rotations applied to
%   all three points.
% \item 
% \end{itemize}

% There are three main points to get across:
% \begin{enumerate}
% \item Why algebraically indexed types?
% \item Why relational parametricity?
% \item Why study them together?
% \end{enumerate}

@@

\begin{itemize}
\item Formulation of a general class of type systems that can either
  be used as programming languages in their own right, or as the
  targets of type-based analyses.
\item A collection of compelling examples of algebraically indexed
  types, including a novel type system for geometry, a refined type
  system for information flow, based on logic, and a simple type
  system for basic continuity analysis.
\item Deduction of useful free theorems in each of our main examples.x
\item A refined relational interpretation in order to derive
  non-definability results. Fixing a minor problem in Kennedy's work.
\end{itemize}

%%% Local Variables:
%%% TeX-master: "paper"
%%% End:
